\textbf{Access Control for Content Distribution Network Assets}

### 2016-04-19 tex/paper.tex
Updated presentation with equation
Updated thesis title

%}}}
\title{\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}}
\author{Klingsbo, Lukas}

@@

\keywords{CDN, Copy-on-Write, Eventual Consistency, MongoDB, Persistent Storage, Scalability, 
Software Security}
\end{abstract}

@@

The research question that this report tries to answer is how and whether it is practically 
feasible to use Copy-on-Write for a high-level system like the one that is implemented and how 
it can affect the system's scalability.

@@

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to affect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept.

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C \cup \{c'\}, F) \xrightarrow{u, create(m,c)} (C \cup \{c \cup \{m\}\}, F \cup \{m.file\})}
\end{equation}
\vspace{1em}

>>>>

%}}}
\title{\textbf{Access Control for Content Distribution Network Assets}}
\author{Klingsbo, Lukas}

@@

\keywords{CDN, Copy-on-Write, Eventual Consistency, MongoDB, Persistent Storage, Scalability, 
Software Security, Access Control}
\end{abstract}

@@

The research question that this report tries to answer is how and whether it is practically 
feasible to use Copy-on-Write for a high-level system like the one that is implemented and how 
it can effect the system's scalability.

@@

\end{description}
\newpage
\section{Model} \label{sec:model}
This section describes how different operations can be expected to effect the data in the system.
The model for this work also shows how the data can only be accessed or modified by
authorized users and how the defined integrity of the data is always kept.

@@

\vspace{2em}
\textbf{File Creation}
\vspace{1em}
\begin{equation} \label{eq:filecreate}
    \inferrule
    {C \ni c \\ A[u,c] \\ m \centernot \in c \\ \neg readOnly(c)} 
    {(C \cup \{c\}, F) \xrightarrow{u, create(m,c)} (C \cup \{c \cup \{m\}\}, F \cup \{m.file\})}
\end{equation}
\vspace{1em}
